\mytitle{}

### 2019-05-03 paper/paper.tex
Reasonable (untested) first attempt at randomised single flow-feature isolation
* With a probability (modifier of current value of epsilon at the agent in question), RL agents can/will now make their decisions based upon a subset of the statespace for the given flow. This SHOULD work to reduce noise substantially, idea courtesy of Cristian Urlea back in February.

* Note: This is very likely to be BROKEN when combned with multiple subactors. I need to re-examine that particular interaction, and store/compute narrowings for each one. Either that, or limit computation to a single subactor when t

@@

>>>>

TCP-Cubic still has a dependence on the $1/p^{0.75}$ -- slightly slower falloff, but still significant \cite{rfc8312}.

@@

?? What other choices did we make? Taking actions with (and updating) fewer tiles according to probability $\epsilon$. Updating all tiles' action value estimates separately to produce different update targets.
